%!TEX root = ../main.tex

% \begingroup
% \newgeometry{left=2.5cm,right=2.5cm,top=2.5cm,bottom=2.5cm}
% \part{Practical Application: Simulation}

% \endgroup

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Case Study}
\label{chap:case-study}

\begin{textblock*}{.7\textwidth}(70mm-\offset,25mm-\offset)
    \begin{fquote}[Narcotics Anonymous]
        Insanity is doing the same thing, over and over again, but expecting different results.
    \end{fquote}
\end{textblock*}

This part of the thesis aims to apply the developed and implemented model to different scenarios in possible interest.
Ideas, that have come up during the implementation and validation of the models, shall be picked up here and used as a demonstration for \textit{diffpssi}
On the other hand they can give more hints and discussion potential for the research questions targeting the \acs{FSM}.
The constituton of the following sections is differing compared to the rest of the thesis.
Each subsection will look at a specific idea or area, where a hypothesis or expectation is presented, the simulation set-up described, and the results drawn.
This deviation targets not to mix the cases or ideas up and to strive for a more consistent argumentation.

\ai{
    Maybe interesting assessment: Can one prevent the forming of one weak bus? 
    -> If the grid is weak, all busses are getting weaker / problematic during a fault. 
    -> But does ONE get weaker than the others? 
    Or can the FSM prevent that and utilize all busses similar?
}

\commenting{
    In the interest of investigation / the Case Study are:
    \begin{itemize}[nosep]
        \item Influence of switching times on stability margin/begin of destabilization,
        \item Influence of max. ratio change per switching event, and
        \item Influence on different test systems (destabilization mechanisms).
    \end{itemize}
}

\commenting{
    Does it make sense to structure like that? (Scenarios - Simulation - Results)
    
    Or is it a better idea thinking in terms of specific \glqq use cases\grqq~as sections:
    \begin{itemize}[nosep]
        \item What happens under strong grid conditions? -> Section: Strong grid condition behavior
        \item What happens under weak grid conditions? -> Section: Weak grid condition behavior
        \item Strongly interconnected grids
        \item Widely extended linear string grids
    \end{itemize}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Practical Application of the FSM in Comparison to the OLTC}

\commenting{
    Here the discussed basic application / simulation with Ilya
    \begin{itemize}[nosep]
        \item FRT curves of the FSM vs OLTC in SMIB with machine controllers
        \item Describe differences, untypical behavior, etc.
        \item Include visualizations, also with FRT curves
        \item Influences of faster response, bigger voltage range, etc.
    \end{itemize}
}
\subsubsection{Objectives and Expectations}

\subsubsection{Simulation Set Up}

\subsubsection{Results}

\subsubsection{Deductions and Futher Improvements}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Influence of FSM on Power or Voltage Swings of Machines}

\commenting{Thinking of Rotor Angle Stability, maybe considered by an EAC implementation?

What does the fast Switching, esp. at up to 8\% of the nominal voltage, do to the machines?

Comparison between standard Transformer / OLTC and FSM control.}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section{Utilization of FSM with a Power Swing Damping Effect}

\commenting{Thinking of the damping effect of the FSM, especially in the case of power swings, caused by shortages and following swinging of Generators.}

\subsubsection{Objectives and Expectations}

\subsubsection{Simulation Set Up}

\subsubsection{Results}

\subsubsection{Deductions and Futher Improvements}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Novel Control Strategy Aspects to a FSM Control}
    
\commenting{
    Thinking of fast and slow voltage gradients: fast gradients are compensated by the FSM, slow gradients are compensated by the OLTC. 
    Therefore optimal utilisation of injected damping moment of the FSM. 
    
    Also thinking of different presets of the OLTC and FSM, which are tried to keep constant. 
    Different grid operators can utilize for typical grid conditions of over- or undervoltage at \acs{PCC}.
    
    Following contains:
    \begin{itemize}
        \item Implemetation of different logic
        \item Testing of presets and switchin logic
        \item Damping moment beneficial?
    \end{itemize}
}

\subsection{Alternative Tap Skipping Logics}

\subsection{Voltage Difference Based Time Constants}

\subsection{Voltage Gradient Based Time Constants}



\subsubsection{Objectives and Expectations}

\subsubsection{Simulation Set Up}

\subsubsection{Results}

\subsubsection{Deductions and Futher Improvements}

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section{Possible Extension for Power Flow Congruent Control}

% \commenting{
%     Extension in the Control Algorithm to decide which Bus has to be regulated, to avoid contrairy actions of the OLTC and FSM against the power flow.
%     Therefore not decrease of stability, but increase. 
%     Possible Application: Grid coupling Transformers, Battery Storage assisted Virtual powerplants, etc.

%     For this thinking maybe another control strategy is relevant:
%     \begin{itemize}[nosep]
%         \item No setpoint from a load flow day-ahead or similar time frame; but rather current load and bus voltages are considered
%         \item Not the deviation of one transformer bus voltage from a setpoint, but the deviation between the two bus voltages is relevant
%         \item Maybe the absolut deviation to the optimal bus voltages at the current load situation is relevant  
%     \end{itemize}

%     Big general problem: In which direction does the OLTC / the FSM have to swith? 
%     In some cases, the direction is not correct, in some it is correct.
% }


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary in Short and Simple Terms}