%!TEX root = ../main.tex

\begingroup
% \RedeclareSectionCommand[beforeskip=3.5cm]{chapter}

\chapter*{Preface}
% \phantomsection\addcontentsline{toc}{chapter}{Preface}

\thispagestyle{empty}

% \begin{textblock*}{.7\textwidth}(70mm,25mm)
%     \begin{fquote}[Albert Einstein]
%         For knowledge is limited to all we know and understand, while imagination embraces the entire world, and all there will be ever to know and understand.
%     \end{fquote}
% \end{textblock*}
\begin{textblock*}{.7\textwidth}(70mm,25mm)
    \prefacelogo
\end{textblock*}

This thesis marks the closing of another exiting chapter in my learning path so far.
It hasn't been straight, and I like it that way.
At first with the vision to become an engineer building cars, the beginning enthusiasm for informatics over a lot of practical experience at my first employer.
Rescuing me in a energy storage topic for my bachelors thesis, gaining more interest, and the idea to pursue a masters course in energy systems.
A lot of persons mentoring me, giving me impulses in every directions, I have to thank at least all of them!
At FAU I was starting over at a completely different level of knowledge and abilities, but I was glad meeting a lot of fellow students helping me.
I have to thank them all for studying with me, enjoying lunch in the mensa or just going out!

When looking into the electrical energy systems side first, I was overwhelmed.
So I started with a student research paper, which was also the base for this thesis and everything that is currently ongoing and will happen in the future.
At this point I have to be very grateful for my supervisors Ilya and Georg.
Always being patient, triggering the right discussions for me, and don't mind explaining some more or less obvious things.
Thank you for your supervision, it was a great time and I hope we can work on things in the future!

The past half year was quite demanding, but one of the steepest learning curves I ever had.
Many thanks to the colleagues at Siemens FT, which help me gain a lot of momentum, and enjoying the way they work there!
As well I have to thank Gregor Becker a lot for discussing with me so many times about ideas, ways to look at problems or even lending a pair of eyes in troubleshooting. 
Thank you as well for proofreading this thesis.

\begin{center}
    - Maximilian Köhler -
\end{center}

\endgroup